%!TEX program = lualatex

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Laila Chavez}
\address{ Seattle, WA 98109}
\contacts{(562) 552-0620 \linebreak lailamay.chavez@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Product Manager}{VueMed}{June 2023 -- December 2023}			
			\begin{itemize}
				\item Led a pilot project as a product manager from design to production, providing a medical organization with ESL labels for inventory management, showcasing strong project management skills and client-focused solutions.
				\item Cleaned client data from Excel spreadsheets and skillfully created a structured SQL database, enhancing internal usage efficiency. 
				\item Designed ESL labels utilizing data from client's inventory item master, demonstrating exceptional attention to detail and client-specific customization.
				\item Spearheaded architectural and design discussions with internal cross-functional teams, facilitating collaborative efforts to align on project goals and strategies.
				\item Effectively managed project progression using Smartsheet and Jira, ensuring timely updates and maintaining transparent communication with stakeholders through regular sync-ups.
				\item Conducted on-site client visits for comprehensive testing of ESL labels and application, meticulously documenting key findings to enhance development processes. 
				\item Authored comprehensive onboarding documentation to streamline the integration process for new team members.
				\item Conducted extensive research and developed detailed Git workflow documentation, standardizing development practices for the growing development team.
				\item Engaged with internal dashboard application users to identify bugs, and efficiently translated feedback into actionable Jira bug stories.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer}{Accenture}{March 2021 -- May 2023}	
			\begin{itemize}
				\item Optimized a monolithic application by breaking it up into microservices, resulting in easier deployments and testing.
				\item Created integration, end-to-end, and unit tests to ensure application and code quality.
				\item Implemented Test Driven Development to develop clean and concise code.
				\item Championed the use of Behavior Driven Development to work with customers to understand the features needed for the product.
				\item Collaborated closely with product owners and internal teams to ensure the solution meets customer standards.
				\item Used technologies such as Angular, React, and Next.js to create modern full-stack web applications.
				\item Modernized web applications using optimization techniques like server side rendering to improve lighthouse performance scores by 25\% providing better user experience.
				\item Utilized agile methodologies to create stories during the software development life cycle using tools such as Jira and Confluence.
				\item Wrote various onboarding documentation to help new developers bootstrap quicker to projects.
				\item Facilitated retro style meetings to gauge team morale and optimize team efficiency with action items. 
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Seattle, WA}{North Seattle College}{Fall 2016 -- June 2020}
			\begin{itemize}
				\item Bachelor of Applied Science in Application Development. GPA: 3.8/4.0.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Irvine, CA}{University of California, Irvine}{Fall 2011 -- September 2015}
			\begin{itemize}
				\item Bachelor of Arts in Cognitive Psychology and Sociology. GPA: 3.7/4.0.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Certifications, Languages, and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item AWS Certified Cloud Practitioner
				\item Python, SQL, MySQL, JavaScript, TypeScript, HTML5, CSS3, GraphQL, C\#
				\item .NET Blazor, React.js, Next.js, Node.js, REST, Angular, Tailwind CSS, Microsoft Azure, AWS
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}

